Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-19 papers/clusters.tex
Added wild speculation about the high-velocity-dispersion cluster

ARC: What can be said about the M 53 stars? Since we find GCs which are
	mostly spatially concentrated (e.g., very few sitting elsewhere),
	and then we find M53 ``co-cluster'' stars all over the halo, does this
	directly speak for evidence of accretion by proto-stellar clusters
	in the high-redshift analogues of the Milky Way?  DWH say: If you use the name ``M53'' then define it or say where you see it.

>>>>

The high-velocity-dispersion structure seen in Figure \ref{halo} stands
in stark contrast to the rest of the clusters we have identified. In
addition to being highly clustered in 15-dimensions, it is visibly
clustered in our 2-d projections. Indeed, it is more clustered in our
abundance projections than the young stellar structure in the disk,
and comparably so to the other known globular clusters that we have
shown here. The disparity between this structure and others presented
here is the lack of co-spatial stars. 12 stars within this cluster are
marked as `M53' candidates by \apogee, but the remaining 145 stars
are spread amongst fields throughout the halo.

% The high-velocity-dispersion structure in the Galaxy halo.
We freely admit that k-means is by no means optimal, and other clusters
we identify are accompanied by a few stars that are not currently co-spatial.
Those stars may be unassociated interlopers that have been misclassified,
or they may be true cluster members that are now unbound. However in the
case of the high-velocity-dispersion structure in Figure \ref{fig:halo},
the situation is far more extreme. We identify a group of stars with
highly similar abundances in 15 dimensions that are now spread throughout
the Galaxy. Because some stars are candidates of the massive globular
cluster M53, it provides tantalizing possibility that these stars may
indeed be all members of the same co-natal gas cloud, implying that 
these stars have been accreted onto the halo by a single globular
cluster early in the Milky Way's formation. While speculative (and we
make no consideration to whether this is indeed the true scenario),
this example demonstrates the ultimate goal of chemical tagging.
